# Process Radtags

Raw reads are checked for barcode indices and RAD cutsite then demultiplexed. A sliding window checks the average quality score and discards those with less than 90% probability of being correct corresponding to a raw phred score of 10. 

```{r}
##############################
## INITIALIZE DIRECTORIES
##############################
# Define directories
home_dir <- "./"
raw_dir <- "./raw/"
int_dir <- "./intermediate/"
# results directories
radtag_dir <- paste0(int_dir,"process_radtags/")
denovo_dir <- paste0(int_dir,"denovomap/")
populations_dir <- paste0(int_dir,"populations/")
```

Load the relevant parameters. Stacks versions 2.65+ are necessary for our analysis as earlier versions do not have the "aclI" enzyme option. 

```{r}
##############################
## PARAMETERS
##############################
# general cutside
renz1 = "pstI"
# rare cutsite
renz2 = "aclI"
# adapter sequence
lenth_limit = 150
```

Identify all of the trimmed files for use as imput.

```{r}
##############################
## LIST FILES
##############################
# list of sequence directories
fq <- list()
list.files(path = raw_dir, pattern = "MK1", include.dirs = T) -> fq
# trimmed P1 reads
p1 <- list()
list.files(path = raw_dir, pattern = "Trim1.fq.gz", recursive = T) -> p1
# trimmer P2 reads
p2 <- list()
list.files(path = raw_dir, pattern = "Trim2.fq.gz", recursive = T) -> p2
```

Repeat the process_radtags function for each sequence directory. All demultiplexed reads are then stored in the same directory, "process_radtags". 

```{r}
##############################
## PROCESS_RADTAGS
##############################
### Run process_radtags to parse the Combined data by individual
for (i in seq_along(fq)){
  system(
    paste0("process_radtags",
           " -1 ",raw_dir,p1[i],
           " -2 ",raw_dir,p2[i],
           " -b ",raw_dir,fq[i],"/barcodes_",fq[i],
           " --paired ",
           " -c ",
           " -r ",
           " -o ",radtag_dir,
           " -q ",
           " --inline-inline ",
           " --renz-1 ",renz1,
           " --renz-2 ",renz2
    ),
    intern = TRUE)
}
```

```{r}
# cleanup
rm(radtag_parameters,p1,p2,i,renz1,renz2,lenth_limit,fq)
```
