# Denovo Map

The denovo_map program executes each of the steps in the Stacks pipeline individually in successive order.

```{r}
##############################
## INITIALIZE DIRECTORIES
##############################
# Define directories
home_dir <- "./"
raw_dir <- "./raw/"
int_dir <- "./intermediate/"
# results directories
radtag_dir <- paste0(int_dir,"process_radtags/")
denovo_dir <- paste0(int_dir,"denovomap/")
populations_dir <- paste0(int_dir,"populations/")
```

A population map contains assignments of each of your samples to a particular population. The number of mismatches allowed between stacks within individuals during ustacks (-M), is iterated to determine which the optimal value might be. Sequence replicates can be used in this case to identify the value with the lowest error rate, otherwise select a single value for -M.

```{r}
##############################
## PARAMETERS
##############################
### load parameters
# load population map
pop_map = paste0(raw_dir,"popmap")
# number of mismatches allowed between stacks within individuals (for ustacks).
M = 4
# the number of threads/CPUs to use (default: 1).
Thread = 10
```

Run denovo_map either iteratively or at a single value. Each value of -M is save to a separate directory.

```{r}
# new list of directories to save results
denovo_M_dir <- list()
## Iterate for variable values of M
for (i in seq_along(M)){
    denovo_M_dir[[i]] <- paste0(denovo_dir,"denovo_M",M[i],"/")
    # empty directory to save FastQ files
    unlink(denovo_M_dir[[i]], recursive = TRUE, force = TRUE)
    dir.create(denovo_M_dir[[i]], showWarnings = FALSE,
               recursive = TRUE)
    system(paste0("denovo_map.pl",
                  " -T ", Thread,
                  " -M ", M[i],
                  " -o ", denovo_M_dir[[i]],
                  " --samples ", radtag_dir,
                  " --popmap ", pop_map,
                  " --paired"
    ), 
    intern = TRUE)
    }
```

```{r}
# cleanup
rm(i,denovo_M_dir,Thread,M,pop_map)
```